### 2018-04-08 reports/thesis/chapters/5_inference.tex
Further modified value and figures output locations.

This method for inference can be applied to the dataset \texttt{Sep16 120deg}. The 20 x-ray images were spilt into 2. 19 images were used to train the variance-mean model. One image, called the test image, was used to compare with \texttt{aRTist}, as shown in Figure \ref{fig:inference_scan_aRTist}.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/scan.eps}
        \caption{X-ray image}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/aRTist.eps}
        \caption{\texttt{aRTist} simulation}
    \end{subfigure}
    }
    \caption{An x-ray scan of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset. This can be compared directly to the \texttt{aRTist} simulation for defects.}
    \label{fig:inference_scan_aRTist}
\end{figure}

For each pixel, a $z_{i,j}$ statistic was calculated. A $z_{i,j}$ statistic too large in magnitude can be considered to be evidence of a positive result. Another way to represent the $z_{i,j}$ statistic is the $p$-value which is given as
\begin{equation}
    p_{i,j} = 2(1-\Phi(\|z_{i,j}\|))
\end{equation}
which can takes values $0\leqslant p_{i,j} \leqslant 1$. A $p$-value too small is considered to be evidence of a positive result. The result $z$ statistics and $p$-values are shown in Figure \ref{fig:logp_z}.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/logp.eps}
        \caption{$-\log p\text{-values}$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/z_image.eps}
        \caption{$z$ statistics}
    \end{subfigure}
    }
    \caption{The resulting z statistics and $p$ values comparing an x-ray scan with the \texttt{aRTist} simulation.}
    \label{fig:logp_z}
\end{figure}

The resulting $z$ statistics and $p$-values are concerning. This is because the $p$-values are not very smooth on the surfaces of the sample. It should be expected that small $p$-values are in areas of the defects. Significant pixels were chosen for $\|z\|>\input{../figures/inference/z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} algorithm at the $z_\alpha = 2$ significance level. The significant pixels are shown in Figure \ref{fig:sig_pixels}.

@@

Model misspecification appears to be the main source of error. The $z$ statistics can be inspected using a histogram or a QQ plot, as shown in Figure \ref{fig:z_histo}. It can be seen that the $z$ statistics do not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect. However this assumption can relaxed and can be done using the empirical null \citep{efron2004large}.

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/inference/sig_pixels.eps}
    \caption{Significant pixels highlighted at the $z_\alpha = 2$ significance level.}
    \label{fig:sig_pixels}
\end{figure}

\begin{figure}
    \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/z_histo.eps}
    	\caption{Histogram}
    \end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/z_qq.eps}
    	\caption{QQ plot}
    \end{subfigure}
	}
    \caption{Distribution of the  $z$ statistics with the BH procedure critical region}
    \label{fig:z_histo}
\end{figure}

>>>>

This method for inference can be applied to the dataset \texttt{Sep16 120deg}. The 20 x-ray images were spilt into 2. 19 images were used to train the variance-mean model. One image, called the test image, was used to compare with \texttt{aRTist}, as shown in Figure \ref{fig:inference_initial_artist_scan_aRTist}.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_scan.eps}
        \caption{X-ray image}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_aRTist.eps}
        \caption{\texttt{aRTist} simulation}
    \end{subfigure}
    }
    \caption{An x-ray scan of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset. This can be compared directly to the \texttt{aRTist} simulation for defects.}
    \label{fig:inference_initial_artist_scan_aRTist}
\end{figure}

For each pixel, a $z_{i,j}$ statistic was calculated. A $z_{i,j}$ statistic too large in magnitude can be considered to be evidence of a positive result. Another way to represent the $z_{i,j}$ statistic is the $p$-value which is given as
\begin{equation}
    p_{i,j} = 2(1-\Phi(\|z_{i,j}\|))
\end{equation}
which can takes values $0\leqslant p_{i,j} \leqslant 1$. A $p$-value too small is considered to be evidence of a positive result. The result $z$ statistics and $p$-values are shown in Figure \ref{fig:inference_initial_artist_logp_z}.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_logp.eps}
        \caption{$-\log p\text{-values}$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_image.eps}
        \caption{$z$ statistics}
    \end{subfigure}
    }
    \caption{The resulting z statistics and $p$ values comparing an x-ray scan with the \texttt{aRTist} simulation.}
    \label{fig:inference_initial_artist_logp_z}
\end{figure}

The resulting $z$ statistics and $p$-values are concerning. This is because the $p$-values are not very smooth on the surfaces of the sample. It should be expected that small $p$-values are in areas of the defects. Significant pixels were chosen for $\|z\|>\input{../tables/initial_artist_z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} algorithm at the $z_\alpha = 2$ significance level. The significant pixels are shown in Figure \ref{fig:inference_initial_artist_sig_pixels}.

@@

Model misspecification appears to be the main source of error. The $z$ statistics can be inspected using a histogram or a QQ plot, as shown in Figure \ref{fig:inference_initial_artist_z_histo}. It can be seen that the $z$ statistics do not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect. However this assumption can relaxed and can be done using the empirical null \citep{efron2004large}.

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/inference/initial_artist_sig_pixels.eps}
    \caption{Significant pixels highlighted at the $z_\alpha = 2$ significance level.}
    \label{fig:inference_initial_artist_sig_pixels}
\end{figure}

\begin{figure}
    \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_histo.eps}
    	\caption{Histogram}
    \end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_qq.eps}
    	\caption{QQ plot}
    \end{subfigure}
	}
    \caption{Distribution of the  $z$ statistics with the BH procedure critical region}
    \label{fig:inference_initial_artist_z_histo}
\end{figure}
